Constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-29 magic_paper.tex

\begin{abstract}
Magic states are key ingredients in schemes to realize universal fault-tolerant quantum computation.
Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms. Here, we develop a statistical mechanical framework based on majorization in which Wigner negative magic states provide non-classical free energy that is processed under Clifford circuits for qudits of odd prime dimension. While traditional free energy is not defined in the presence of negativity, we show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds. These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can incorporate hardware physics, such as temperature dependence and physical Hamiltonians. We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic. We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting. This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
\end{abstract}

@@

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.35]{figs/distill_bounds.pdf}
    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols. The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})). The bound $R_\infty$ follows from a Lorenz curve analysis presented in Sec.~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Sec.~\ref{section:entropies}. Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints. The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with neither of $\r,\r'$ having negative components then it can be shown~\cite{ruch_mixing_1978} that
\begin{equation*}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
\end{equation*}
for all $x \in [0,1]$.
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

@@

Distillation bounds can be obtained from any location of the Lorenz curve, including the region around the peak, by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output. In particular a simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.

The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use Proposition~\ref{prop:first_elb} in the appendices, to bound $R(\epsilon, \epsilon')$. We find that
\begin{equation}\label{eq:unital-bound}
	R(\epsilon, \epsilon') \leq R_\infty \coloneqq\frac{\log (3-4\epsilon)}{\log (3-4\epsilon')}.
\end{equation}
The choice of denoting the bound by $R_\infty$ is explained in Sec.~\ref{section:entropies} in relation to single-shot entropies. For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\log (1 - \frac{4}{3} \epsilon)}{\log 3}.
\end{equation}
We compare this to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\log \left(1 - \frac{8}{15}\epsilon \right)}{\log \frac{5}{3}}.
\end{equation}
The recently introduced max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in Fig.~\ref{fig:distill_bounds}.

@@

The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy is not well-defined, however it diverges in a well-defined way. We can write the divergence of the entropy as 
\begin{equation}
	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\bmz} |W_\rho (\bmz)|^{1+\epsilon}
\end{equation} 
with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, so we obtain a second new perspective on mana:
\begin{equation}\label{eq:mana-divergence}
\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1+\epsilon}(W_\rho).
\end{equation}
Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.

@@

We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
\begin{theorem}\label{thm:entropic_bounds}
	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit. Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
	\begin{equation}
		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
	\begin{equation}
\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
\end{equation}
between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
\end{theorem}
The proof is given in Appendix~\ref{app:single-shot}.

@@

If correlations in $\tau'_m$ between subsystems can be neglected, then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ and
\begin{equation}
	\widetilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}),
\end{equation}
which gives a generalized version of Theorem~\ref{thm:free-energy}.

We can illustrate a simple application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
\begin{equation}
	R \leq R_\alpha=\frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq R_\alpha=\frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
This upper bound can be numerically minimized over $\alpha$, for any $\epsilon$. The case $R_{10}$ is shown in Fig.~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.

@@

The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization. This would correspond to transformations that are \emph{not} unital, but still respect the symplectic structure. Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}. While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of classical statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit. Statistical mechanics of actual systems obey Hamiltonian dynamics, thus they automatically respect a symplectic form~\cite{Arnold_2000, Pathria_1997}. Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition. Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g. for a particle on a ring) or by first studying the discrete case. Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is another regime where these techniques could be of use.

@@

3. Given a vector $\w \in \mathbb{R}^N$, it is generally the case that $\max_k w_k \ne \max_k |w_k|$. 
However, we do have that
\begin{equation}
	\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_{k_1,k_2} |w_{k_1} w_{k_2}|,
\end{equation}
and if additionally $w_k \geq 0$ for all $k$, then we also have for even $n$ that
\begin{equation}
	\max_{k_1, k_2, \dots, k_n} \left( w_{k_1}w_{k_2}\cdots w_{k_n} \right) = (\max_k |w_k|)^n.
\end{equation}
Therefore, for arbitrary $\w \in \mathbb{R}^N$ and $n$, we have
\begin{align}
	&\max_{k_1, k_2, \dots, k_{2n}}\left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = \nonumber\\
	&\max_{k_1, k_2, \dots, k_{2n}}\left( |w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}}w_{k_{2n}}| \right) = \nonumber \\
	&\left( \max_{k_1 ,k_2}\left( w_{k_1} w_{k_2} \right) \right)^n.
\end{align}

@@

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which implies that
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i}(\w) \leq \frac{\partial H_\alpha}{\partial w_j}(\w),
\end{equation}
for any $\w$ in the interior of $\mathcal{Q}_N^\downarrow$.
Therefore, $H_\alpha$ is Schur-concave on $\mathcal{Q}_N$ and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
\end{proof}
While we have integers $a,b$ such that $0 < \alpha=\frac{2a}{2b-1} < 1$ and $H_\alpha(\w)$ is well-defined, it turns out that monotonicity does not hold if we drop the condition $a \ge b$. If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) \coloneqq \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$. As an analogy, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.

@@

	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. 
	Then, $D_\alpha$ is Schur-convex, i.e. $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.

@@

@@

\begingroup
\def\thetheorem{\ref{thm:entropic_bounds}}
\begin{theorem}
	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit. Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
	\begin{equation}
		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
	\begin{equation}
\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
\end{equation}
between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
\begin{proof}
	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi diveregence, proven in Theorem~\ref{thm:Da_props}.

>>>>

\begin{abstract}
Magic states are key ingredients in schemes to realize universal fault-tolerant quantum computation.
Theories of magic states attempt to quantify this computational element via monotones and determine how these states may be efficiently transformed into useful forms. Here, we develop a statistical mechanical framework based on majorization to describe Wigner negative magic states for qudits of odd prime dimension processed under Clifford circuits. We show that majorization allows us to both quantify disorder in the Wigner representation and derive magic distillation bounds. These upper bounds are shown to be tighter than other bounds, such as from mana and thauma, and can be used to incorporate hardware physics, such as temperature dependence and system Hamiltonians. We also show that a subset of single-shot R\'{e}nyi entropies remain well-defined on quasi-distributions, are fully meaningful in terms of data processing and can acquire negative values that signal magic. We find that the mana of a magic state is the measure of divergence of these R\'{e}nyi entropies as one approaches the Shannon entropy for Wigner distributions, and discuss how distillation lower bounds could be obtained in this setting. This use of majorization for quasi-distributions could find application in other studies of non-classicality, and raises novel questions in the context of classical statistical mechanics.
\end{abstract}

@@

\begin{figure}[t]
    \centering
    \includegraphics[scale=0.38]{figs/distill_bounds.pdf}
    \caption{\textbf{Magic distillation bounds from majorization of Wigner quasi-distributions.} The above plot shows distillation upper bounds for qutrits obtained from majorization on unital protocols. The constraints are plotted as a function of the depolarizing error $\epsilon$ for a noisy Strange state (Eq.~(\ref{eq:noisysn})). The bound $R_\infty$ follows from a Lorenz curve analysis presented in Sec.~\ref{sec:unital}, while the bound $R_{10}$ comes from single-shot entropies on the Wigner quasi-distributions, as discussed in Sec.~\ref{section:entropies}. Numerical bounds $R_{\rm{num}}$ are obtained by using the full set of majorization constraints. The new bounds $R_\infty$, $R_{10}$, $R_{\rm{num}}$ all provide stricter constraints than mana~\cite{cit:veitch2} and max--thauma $\theta_{\rm{max}}$~\cite{Wang_2020} bounds for noisy Strange states.
    }
    \label{fig:distill_bounds}
\end{figure}

@@

In the usual case where $\w$ and $\r$ are both probability distributions the Lorenz curve is defined on the interval $[0,1]$, and rises monotonically until it reaches the value $1$ at $x=1$. The value $L_{\w|\r}(x) = 1$ is a global maximum. Moreover, if $\w, \w', \r, \r'$ are all valid probability distributions with $\r,\r'$ having positive components then it can be shown~\cite{ruch_mixing_1978} that
\begin{equation*}
(\w, \r) \succ (\w', \r') \mbox{ if and only if } L_{\w |\r}(x) \ge L_{\w' |\r'}(x),
\end{equation*}
for all $x \in [0,1]$.
This provides a simple way of computing whether relative majorization holds between pairs of probability distributions.

@@

Distillation bounds can be obtained from any part of the Lorenz curve by imposing the constraint that the Lorenz curve of the input state never dips below the curve of the output. One simple constraint can be obtained by considering the initial slopes of the two Lorenz curves.

The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by requiring that the initial slope for the input state Lorenz curve is larger than that of the output state (Proposition~\ref{prop:first_elb} in the appendices) we find that
\begin{equation}\label{eq:unital-bound}
	R(\epsilon, \epsilon') \leq R_\infty \coloneqq\frac{\log (3-4\epsilon)}{\log (3-4\epsilon')}.
\end{equation}
The choice of denoting the bound by $R_\infty$ is explained in Sec.~\ref{section:entropies} in relation to single-shot entropies. For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\log (1 - \frac{4}{3} \epsilon)}{\log 3}.
\end{equation}
We compare this to other known distillation bounds coming from mana and thauma. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\log \left(1 - \frac{8}{15}\epsilon \right)}{\log \frac{5}{3}}.
\end{equation}
The max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in Fig.~\ref{fig:distill_bounds}.

@@

The $\alpha \rightarrow 1$ limit of the R\'{e}nyi entropy diverges if negativity is present, however it diverges in a well-defined way. We can write the entropy as 
\begin{equation}
	H_{1+\epsilon}(W_\rho) = -\epsilon^{-1} \log \sum_{\bmz} |W_\rho (\bmz)|^{1+\epsilon}
\end{equation} 
with $\epsilon \rightarrow 0^+$ through a sequence of rational values. We recall that mana can be written as $\M(\rho) = \log \sum_{\bmz} |W_\rho(\bmz)|$, so we obtain a second new perspective on mana:
\begin{equation}\label{eq:mana-divergence}
\M(\rho) = -\lim_{\epsilon \rightarrow 0^+} \epsilon H_{1+\epsilon}(W_\rho).
\end{equation}
Therefore, the mana of a state $\rho$ is the residue of a pole in $H_\alpha(W_\rho)$, and quantifies the divergence of the R\'{e}nyi-entropy as we approach the limiting Shannon entropy $H(W_\rho)$.

@@

We can now apply this to obtain a family of magic distillation bounds based on R\'{e}nyi divergences.
\begin{theorem}\label{thm:entropic_bounds}
	Consider a general magic state distillation protocol on odd prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit. Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
	\begin{equation}
		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.2ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
	\begin{equation}
\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
\end{equation}
between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
\end{theorem}
The proof is given in Appendix~\ref{app:single-shot}.

@@

If correlations in $\tau'_m$ between subsystems can be neglected, then $\tau'_m = \tau'^{\otimes m}$ for some qudit state $\tau'$ and
\begin{equation}
	\widetilde{D}_\alpha( \rho', \tau') = D_\alpha (W_{\rho'} \hspace{1pt}||\hspace{1pt} W_{\tau'}),
\end{equation}
which gives a generalized version of Theorem~\ref{thm:free-energy}, with a term such as $D_\alpha(W_\rho ||W_\tau)$ that behaves essentially as an $\alpha$--free energy difference~\cite{Brandao_2015} in the Wigner representation.

We can illustrate a basic application of the above bound for magic protocols that give unital maps. In this case it is easy to see that the above bound reduces to the simple form
\begin{equation}
	R \leq R_\alpha=\frac{2\log d - H_{\alpha}(W_\rho)}{2\log d - H_{\alpha}(W_{\rho'})}.
\end{equation}
In particular for the case of noisy Strange states on qutrits and $\epsilon'=0$, this bound becomes
\begin{equation}
	R \leq R_\alpha=\frac{2(1-\alpha)\log 3 - \log \left [8(\frac{1}{6} - \frac{\epsilon}{18})^\alpha + (-\frac{1}{3} + \frac{4\epsilon}{9})^\alpha\right ] }{2(1-\alpha)\log 3 + \alpha \log 6 - \log (8 + 2^\alpha )}.
\end{equation}
This upper bound can be numerically minimized over $\alpha$, for any $\epsilon$. The case $R_{10}$ is shown in Fig.~\ref{fig:distill_bounds} and numerical evidence shows it is close to the optimal bound from majorization.

@@

The topic of $G$--majorization has been extensively studied, but to our knowledge there has not been work on relative $G$--majorization. This would correspond to transformations that are not unital. Physically, this regime would correspond to a form of thermo-majorization obtained from looking at the action of the Clifford group at a micro-canonical level, and then reducing to a small subsystem~\cite{Pathria_1997}. While this seems like a painful thing to consider, there is motivation for this beyond the aim of magic protocols: in the case of classical statistical mechanics on a phase space this is precisely the situation, albeit in the continuum limit. Statistical mechanics of actual systems obey Hamiltonian dynamics, thus they automatically respect a symplectic form~\cite{Arnold_2000, Pathria_1997}. Therefore, the pre-order of statistical mechanical states with respect to phase space dynamics preserving a Gibbs state must correspond to a symplectic majorization condition. Of course, technical features arise in the continuum limit when considering distributions on an unbounded phase space, but this could be remedied by either considering a compact phase space (e.g.~for a particle on a ring) or by first studying the discrete case. Such scenarios also arise in the Quantum Hall Effect~\cite{Klitzing_1980}, which is another regime where these techniques could be of use.

@@

3. Given a vector $\w \in \mathbb{R}^N$, it is generally the case that $\max_k w_k \ne \max_k |w_k|$. 
However, we do have that
\begin{equation}
	\max_{k_1,k_2} (w_{k_1} w_{k_2}) = \max_{k_1,k_2} |w_{k_1} w_{k_2}|,
\end{equation}
and if additionally $w_k \geq 0$ for all $k$, then we also have for $2n$ copies that
\begin{equation}
	\max_{k_1, k_2, \dots, k_{2n}} \left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = (\max_k |w_k|)^{2n},
\end{equation}
and also,
\begin{align}
	&\max_{k_1, k_2, \dots, k_{2n}}\left( w_{k_1}w_{k_2}\cdots w_{k_{2n}} \right) = \nonumber\\
	&\max_{k_1, k_2, \dots, k_{2n}}\left( |w_{k_1}w_{k_2}|\cdots |w_{k_{2n-1}}w_{k_{2n}}| \right) = \nonumber \\
	&\left( \max_{k_1 ,k_2}\left( w_{k_1} w_{k_2} \right) \right)^n.
\end{align}

@@

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which implies that
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i}(\w) \leq \frac{\partial H_\alpha}{\partial w_j}(\w),
\end{equation}
for any $\w$ in the interior of $\mathcal{Q}_N^\downarrow$.
Therefore, $H_\alpha$ is Schur-concave on $\mathcal{Q}_N$ and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$ that obey $\w \succ \w'$.
\end{proof}
While we have integers $a,b$ such that $0 < \alpha=\frac{2a}{2b-1} < 1$ and $H_\alpha(\w)$ is well-defined, it turns out that monotonicity does not hold if we drop the condition $a \ge b$. If $\alpha =2a/(2b-1)$ with $\alpha < 1$, then $g(w) \coloneqq \frac{-w^{\alpha-1}}{\alpha-1}$ is no longer monotonic for all $w \in \mathbb{R}$, and the problem occurs when comparing $w_i < 0$ and $w_j >0$. As an example of this dependence of monotonicity on the domain of the function, consider the function $g(x) = \frac{1}{x^3}$ which is monotone decreasing on both $x<0$ and $x>0$ separately, however it is not monotone on the full real-line.

@@

	Let $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$. Let $\w \in \mathcal{Q}_N$, $\w' \in \mathcal{Q}_{N'}$ and $\r \in  \mathcal{Q}^+_N$, $\r' \in \mathcal{Q}^+_{N'}$ with positive rational components $a_i/K$ and $a'_i/K$ respectively.
	Then $D_\alpha(\w \hspace{1pt}||\hspace{1pt} \r) \geq D_\alpha(\w' \hspace{1pt}||\hspace{1pt} \r')$, whenever $(\w, \r) \succ (\w', \r')$.

@@

Since the rationals are dense in the real numbers we can assume any Wigner distribution considered has rational components without affecting results.

@@

\begingroup
\def\thetheorem{\ref{thm:entropic_bounds}}
\begin{theorem}
	Consider a general magic state distillation process on prime dimension qudits, that converts a magic state $\rho^{\otimes n} \longrightarrow \E(\rho^{\otimes n})=\rho'^{\otimes m}$and let $\tau$ be any full-rank stabilizer reference state on a qudit. Then the distillation rate $R \coloneqq m/n$ is upper bounded as,
	\begin{equation}
		R \leq \frac{D_{\alpha}(W_\rho \hspace{1pt}||\hspace{1pt} W_\tau)}{\rlap{\raisebox{-0.1ex}{$\widetilde{\phantom{D}}$}}D_\alpha( \rho', \tau')}
	\end{equation}
	where $\alpha = \frac{2a}{2b-1}$ for any positive integers $a,b$ with $a \geq b$ and the average divergence
	\begin{equation}
\widetilde{D}_\alpha( \rho', \tau') \coloneqq \frac{1}{m} D_\alpha (W_{\rho'^{\otimes m}} \hspace{1pt}||\hspace{1pt} W_{\tau'_m}),
\end{equation}
between the output magic state $\rho'^{\otimes m}$ and $\tau'_m = \E(\tau^{\otimes n})$.
\end{theorem}
\addtocounter{theorem}{-1}
\endgroup
\begin{proof}
	The bound is a direct consequence of the properties of the $\alpha$--R\'{e}nyi divergence in Theorem~\ref{thm:Da_props}.
